A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-06-03 src/paper.tex
Introduction finished

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by the interactions of millions of viewers can provide valuable information for content providers (CPs) to improve their services and improve audience~\cite{Teixeira2010}.

@@

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions from each individual viewer in iTV environments. Thus, iTV applications and services can be developed to obtain viewers' interaction data. Examples of these applications include rating TV programs, amount of viewers, and user profiles.

% In order to support millions of viewers, this architecture was implemented under a cloud based platform

By using proper machine learning algorithms, the captured data can reveal valuable information about viewers' tastes and behaviors~\cite{Kim2012,Shin2009}.

% The approach described in this paper is based on the development of web services that provide means to access content from the CP and

% Since, each viewer has its own personal device as secondary screen

Data about viewers' interactions are captured by personal devices (e.g., smartphones and tablets) that are used to mediate the interaction between viewers and the iTV device.

Personal devices (e.g., smartphones and tablets) are almost ubiquitous and present rich interactive capabilities.

Secondary screen devices arise as a powerful mechanism to accurately identify viewers and  capture their interactions. In this research field, a typical approach is to use personal devices (e.g., smartphones and tablets) as secondary screens~\cite{Courtois2012}, since they are almost ubiquitous and present good graphical capabilities. The connectivity capabilities of smartphones were used in~\cite{Cabarcos2011}, where the Bluetooth technology was used to detect nearby users. With respect to interaction capture, an approach described in~\cite{Teixeira2010} has shown an architecture to capture contextualized viewers interactions through a conventional RC.

\blurb{Achei que o inicio da introducao esta com muito bla bla bla. Tente ir direto ao ponto, dando uma visao geral da sua abordagem, as vantagens e desvantages com as outras abordagens existentes na literatura e as principais contribuicoes do seu trabalho. Por que voce acredita que os revisores devem aceitar o seu trabalho? Qual eh a inovacao? Quais sao as contribuicoes? Quais sao as diferencas para os trabalhos que ja existem. Diminua o bla bla bla do inicio e tente responder estas perguntas na introducao do seu trabalho.}

\section{Secondary Screen Architecture and Implementation}

\blurb{Tente colocar um nome mais sugestivo para esta secao, em vez ``Architecture'' somente.}

@@

\blurb{Tens algum resumo dos resultados experimentais?}

@@

\blurb{Seria bom incluir algum resultado de experimento na conclusao}

>>>>

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by the interactions of millions of viewers can provide valuable information for content providers (CPs) to improve their services~\cite{Teixeira2010}.

@@

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions from each active viewer in iTV environments. By using proper machine learning algorithms, the personal data can reveal important information about viewers' tastes~\cite{Kim2012,Shin2009}.

Since personal devices are almost ubiquitous, they stand out as a powerful mechanism to identify viewers by means of wireless communication technologies~\cite{Cabarcos2011}. In the architecture described in this paper, personal devices play an additional role as a medium of interaction since they are easy and intuitive to use in iTV environments, as pointed out in~\cite{Courtois2012}. An approach described in~\cite{Teixeira2010} has shown an architecture to capture viewers' interactions through a conventional RC. The architecture described in this paper goes further and captures individual and contextualized data. Since the TV environment is shared, the data about nearby viewers is captured to contextualize the interaction with the purpose of helping to infer the behaviors of one viewer toward others ones.

% In order to support millions of viewers, this architecture was implemented under a cloud computing based platform.

% Data about viewers' interactions are captured by personal devices (e.g., smartphones and tablets) that are used to mediate the interaction between viewers and the iTV device.

% \blurb{Achei que o inicio da introducao esta com muito bla bla bla. Tente ir direto ao ponto, dando uma visao geral da sua abordagem, as vantagens e desvantages com as outras abordagens existentes na literatura e as principais contribuicoes do seu trabalho. Por que voce acredita que os revisores devem aceitar o seu trabalho? Qual eh a inovacao? Quais sao as contribuicoes? Quais sao as diferencas para os trabalhos que ja existem. Diminua o bla bla bla do inicio e tente responder estas perguntas na introducao do seu trabalho.}

\section{Secondary Screen Architecture}

@@

% \blurb{Tens algum resumo dos resultados experimentais?}

@@

% \blurb{Seria bom incluir algum resultado de experimento na conclusao}
